---
title: "Comparisons of sample coverages using iNext"
author: "Bernd Panassiti"
date: 'created: 07.06.2023, last modified: `r format(Sys.Date(), format="%d.%m.%Y")`'
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir='../')                     # definining working directory; or normalizePath('../')
opts_chunk$set(fig.align='center',                # aligns all figures
                echo=FALSE,                       # shows r-code
                results='hide',                    # don't display results
                message=FALSE,                    # suppresses library outputs
                warnings=FALSE,                   # suppresses library outputs
                fig.show ='hide',
                tidy=TRUE,  # prevents the source code from running off a pdf page
                dev='pdf')                        # pdf device
```


For installation of iNEXT.beta3D:

https://github.com/AnneChao/iNEXT.beta3D


```{r load,, warning=FALSE}
#Install/load pacman
if(!require(pacman)){install.packages("pacman");require(pacman)}
#Install packages
p_load("tidyverse","vegan","reshape2","magrittr","caret","ggplot2",
       "iNEXT","iNEXT.beta3D","data.table",
       "FD","gawdis")
source("r-code/00_functions.R")
load("data/rawdata.RData")
```

# Introduction
The co-occurrence dataset contains data on **pol**linators (wildbees, butterflies, hoverflies) and **phy**tophagous species (planthoppers).  
  
The following data are available:  

* year: **pol** (2021,2022), **phy** (2021)
* survey periods: **pol** (1,2), **phy** (2)
* treatments: control, early, late

Create list to save the following datasets:
* alpha TD
* alpha PD
* alpha FD
* beta TD
* beta PD
* beta FD

Warning message due to "future" package
https://github.com/satijalab/seurat/issues/3622
options(future.rng.onMisuse="ignore")


# Data preparation
# TD dataframe
```{r}
dfHymenoptera = bee.abund %>%
  dplyr::group_by(species,plot_id)  %>%
  dplyr::summarise(count=sum(count))

beeAbuTD = data.frame(reshape::cast(dfHymenoptera,species~plot_id,fill=0))
rownames(beeAbuTD) = beeAbuTD[,1]
beeAbuTD = beeAbuTD[,-1]

# save plots with 0 species
plots0speciesTD = names(which(apply(beeAbuTD,2,function(x) length(which(x>0)))==0))
```


# PD
## check for same species names with trait matrix
```{r}
beeAbuPD = beeAbuTD

iTree = beeTreeComm
iTree$node.label =  paste("match",rep(1:length(iTree$node.label)),sep="_")


# which species in in bee dataframe are not in tree
beeAbuPDTree = beeAbuPD[-which(!rownames(beeAbuPD) %in% iTree$tip.label),]

# cbind(1:ncol(beeAbuPD),apply(beeAbuPD,2,function(x) length(which(x>0))))
# remove plots 1 species

beeAbuPD = beeAbuPDTree[,-which(apply(beeAbuPDTree,2,function(x) length(which(x>0)))<2)]

# remove plots 1 species
plots0speciesPD = names(which(apply(beeAbuPDTree,2,function(x) length(which(x>0)))==0))
plots1speciesPD = names(which(apply(beeAbuPDTree,2,function(x) length(which(x>0)))==1))
```


# FD
## check for same species names with trait matrix
```{r}
beeAbuFD = beeAbuTD

iTraits = wildbeeTraits
iTraits$species = gsub(" ","_",wildbeeTraits$species) # recode species names with underline

# which species in in bee dataframe are not in traits
beeAbuFDTrait = beeAbuFD[-which(!rownames(beeAbuFD) %in% iTraits$species),]

# cbind(1:ncol(beeAbuFD),apply(beeAbuFD,2,function(x) length(which(x>0))))
# remove plots with 0 or 1 species

beeAbuFD = beeAbuFDTrait[,-which(apply(beeAbuFDTrait,2,function(x) length(which(x>0)))<2)]

plots0speciesFD = names(which(apply(beeAbuFDTrait,2,function(x) length(which(x>0)))==0))
plots1speciesFD = names(which(apply(beeAbuFDTrait,2,function(x) length(which(x>0)))==1))




# which species in traits are not in bee dataframe
iTraits = iTraits[-which(!iTraits$species %in% rownames(beeAbuFD)),]


# rownames(iTraits) = iTraits$species
# beeAbu_distM <- FD::gowdis(iTraits[,-c(1:2)])
beeAbu_distM <-data.frame(StatMatch::gower.dist(iTraits[,-c(1:2)]))
colnames(beeAbu_distM) =  iTraits$species
rownames(beeAbu_distM) =  iTraits$species
```


# Save all datasets in list
```{r}
beeInput = list(
  beeAbuTD = beeAbuTD,
  beeAbuPD = beeAbuPD,
  beeAbuFD = beeAbuFD,
  iTree = iTree,
  iDistM = beeAbu_distM,
  plots1speciesPD = plots1speciesPD,
  plots0speciesPD = plots0speciesPD,
  plots1speciesFD = plots1speciesFD,
  plots0speciesFD = plots0speciesFD)
```

# Calculate estimates
```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)

out.TD <- iNEXT.3D::estimate3D(data = beeInput$beeAbuTD, diversity = "TD", 
               q = 0, datatype = "abundance", 
               base = "coverage", level = 0.7,
               nboot = 30)



out.FD <- iNEXT.3D::estimate3D(data = beeInput$beeAbuFD, diversity = "FD", 
               q = 0, datatype = "abundance", 
               FDdistM = beeInput$iDistM,
               base = "coverage", level = 0.7,
               nboot = 30)
```


Warnings for TD
 In EstiBootComm.Ind(x_) :
  This site has only one species. Estimation is not robust.




rm(.Random.seed, envir=globalenv())
set.seed(2023)

out.PD1 <- iNEXT.3D::estimate3D(data = beeInput$beeAbuPD[,1:40], diversity = "PD", 
               q = c(0,1,2), datatype = "abundance", 
               PDtree = beeInput$iTree,
               base = "coverage", level = 0.7,
               nboot = 2)

out.PD2 <- iNEXT.3D::estimate3D(data = beeInput$beeAbuPD[,41:78], diversity = "PD", 
               q = c(0,1,2), datatype = "abundance", 
               PDtree = beeInput$iTree,
               base = "coverage", level = 0.7,
               nboot = 2)
```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)

outPDtmp = list()
for (i in 1:ncol(beeInput$beeAbuPD)){
dat = data.frame(beeInput$beeAbuPD[,i])
rownames(dat) = rownames(beeInput$beeAbuPD)

try(outPDtmp[[i]] <- iNEXT.3D::estimate3D(data = dat, diversity = "PD", 
               q = 0, datatype = "abundance", 
               PDtree = beeInput$iTree,
               base = "coverage", level = 0.7,
               nboot = 30))


try(
  outPDtmp[[i]]$Assemblage <- colnames(beeInput$beeAbuPD)[i]
  ,silent=TRUE)
  
print(i)}


# Fehler in if (refC > cvrg) { : Fehlender Wert, wo TRUE/FALSE nötig ist


# generate estimates for sites with errors with set.seed(2023)
newID = which(!lengths(outPDtmp))
# newID
#  7  8  9 12 13 16 27 33 50

df = beeInput$beeAbuPD



outNewID=list()
for (i in 1:length(newID)){
j=0
out.id=list()

while(length(which(lengths(out.id)!=0))<1){
j=j+1
rm(.Random.seed, envir=globalenv())
set.seed(j)
dat = data.frame(df[,newID[i]])
rownames(dat) = rownames(df)

try(out.id[[j]] <- iNEXT.3D::estimate3D(data = dat, diversity = "PD", 
               q = 0, datatype = "abundance", 
               PDtree = beeInput$iTree,
               base = "coverage", level = 0.7,
               nboot = 30))
}
out.id[[length(out.id)]]$Assemblage = colnames(df)[newID[i]]
outNewID[[i]] = out.id
print(newID[i])}

# combine both list

outList1 = outPDtmp[!unlist(lapply(outPDtmp,is.null))]
outList1DF = do.call(rbind, outList1)

outList2 = lapply(outNewID, function(x) x[!unlist(lapply(x,is.null))])
outList2DF = do.call(rbind, lapply(outList2, `[[`, 1))


out.PD = bind_rows(outList1DF,outList2DF)

#save seed
seedPD = data.frame(
  plot_id =colnames(beeInput$beeAbuPD)[newID],
  newSeed=unlist(lapply(outNewID, function(x) which(!unlist(lapply(x,is.null)))))
  
)
```

```{r}
bee.TD = out.TD
bee.PD = out.PD
bee.FD = out.FD
```



# Combine all datasets
```{r}
out1 = out.TD %>% dplyr::mutate(diversityType ="TD")  %>%
                  dplyr::select(plot_id = Assemblage,diversityType,
                         qHill = Order.q, obs = m, 
                         estimate = qTD, sd= s.e., lowCI = qTD.LCL, highCI= qTD.UCL,
                         sampleCoverage = SC,method = Method)
                  

out2 = out.PD %>% dplyr::mutate(diversityType ="PD")  %>%
                  dplyr::select(plot_id = Assemblage,diversityType,
                         qHill = Order.q, obs = m, 
                         estimate = qPD, sd = s.e., lowCI = qPD.LCL, highCI = qPD.UCL,
                         sampleCoverage = SC,method = Method)

out3 = out.FD %>% dplyr::mutate(diversityType ="FD")  %>%
                  dplyr::select(plot_id = Assemblage,diversityType,
                         qHill = Order.q, obs = m, 
                         estimate = qFD, sd = s.e., lowCI = qFD.LCL, highCI = qFD.UCL,
                         sampleCoverage = SC,method = Method)

out = as_tibble(bind_rows(out1,out2,out3))


##FD

# plots1speciesFD 
a = length(plots1speciesFD)
out.FD1 = data.frame(plot_id=plots1speciesFD,diversityType = rep("FD",a),qHill = rep(0,a),
                     obs=rep(1,a),
                     estimate=rep(1,a),
                     sd=rep(NA,a),lowCI=rep(NA,a),highCI=rep(NA,a),
                     sampleCoverage = rep(0.7,a),
                     method=rep("Observed",a))

# plots0speciesFD
a = length(plots0speciesFD)

out.FD0 = data.frame(plot_id=plots0speciesFD,diversityType = rep("FD",a),qHill = rep(0,a),
                     obs=rep(0,a),
                     estimate=rep(0,a),
                     sd=rep(NA,a),lowCI=rep(NA,a),highCI=rep(NA,a),
                     sampleCoverage = rep(0.7,a),method=rep("Observed",a))


##PD

# plots1speciesPD 
a = length(plots1speciesPD)

out.PD1 = data.frame(plot_id=plots1speciesPD,diversityType = rep("PD",a),qHill = rep(0,a),
                     obs=rep(1,a),
                     estimate=rep(1,a),
                     sd=rep(NA,a),lowCI=rep(NA,a),highCI=rep(NA,a),
                     sampleCoverage = rep(0.7,a),method=rep("Observed",a))

# plots0speciesPD
a = length(plots0speciesPD)

out.PD0 = data.frame(plot_id=plots0speciesPD,diversityType = rep("PD",a),qHill = rep(0,a),
                     obs=rep(0,a),
                     estimate=rep(0,a),
                     sd=rep(NA,a),lowCI=rep(NA,a),highCI=rep(NA,a),
                     sampleCoverage = rep(0.7,a),method=rep("Observed",a))



#beeDiversity = list()
beeDiversity = dplyr::bind_rows(out,out.PD1,out.PD0,out.FD1,out.FD0)

beeDiversity$site_id = as.character(sapply(beeDiversity$plot_id, function(x) str_split(x,"_")[[1]][1]))
beeDiversity$survey_period = as.character(sapply(beeDiversity$plot_id, function(x) str_split(x,"_")[[1]][2]))
beeDiversity$year = as.integer(sapply(beeDiversity$plot_id, function(x) str_split(x,"_")[[1]][3]))
beeDiversity$grazingTime = as.character(sapply(beeDiversity$plot_id, function(x) str_split(x,"_")[[1]][4]))

beeDiversity %<>% dplyr::arrange(year,site_id,survey_period,grazingTime)
```


# save
```{r}
save(beeInput,
     beeDiversity,
     bee.TD,bee.FD,bee.PD,
     file="results/iNEXT3d_bee.RData")
```

