---
title: "iNEXT link - Butterfly-plant-interactions"
author: "Bernd Panassiti"
date: 'created: 20.01.2022, last modified: `r format(Sys.Date(), format="%d.%m.%Y")`'
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir='../')                     # definining working directory; or normalizePath('../')
opts_chunk$set(fig.align='center',                # aligns all figures
                echo=TRUE,                        # shows r-code
                message=FALSE,                    # suppresses library outputs
                warnings=FALSE,                   # suppresses library outputs
                tidy=TRUE,  # prevents the source code from running off a pdf page
                dev='pdf')                        # pdf device
```


# Introduction
This script calculates alpha-diversity using taxonomic (TD), phylogenetic (PD) and functional (FD) information on butterfly-plant networks.

Useful links:
http://chao.stat.nthu.edu.tw/wordpress/software_download/inext-link/
https://github.com/AnneChao/iNEXT.link
http://chao.stat.nthu.edu.tw/wordpress/wp-content/uploads/software/A%20Quick%20Introduction%20to%20iNEXT.link%20via%20Examples.html


# Loading data and packages
Install the following packages from Anne Chao's github
library(devtools)

install_github('AnneChao/iNEXT.3D')
install_github('AnneChao/iNEXT.4steps')
install_github('AnneChao/iNEXT.beta3D')
install_github('AnneChao/iNEXT.link')

```{r}
#Install/load pacman
if(!require(pacman)){install.packages("pacman");require(pacman)}
#Install packages
p_load("iNEXT.link","iNEXT.3D","ggplot2","dplyr","magrittr")

source("r-code/00_functions.R")
load("data/workingdata.RData")
```

# Data preparation

```{r}
pTraits = pollinatorPlantTraits[,-1] # only remove id column, not species column
iTraits = butterflyTraits[,-1] # only remove id column, not species column
iTree = butterflyTreeNet
pTree = plantTreeNet

out = iNext.link.dataprep(cooccDF = butterfly.coocc[1:3],
                          nTreatments = 3, 
                          iTree = iTree, pTree = pTree,
                          iTraitDF = iTraits, pTraitDF = pTraits)
```

Information on TD input data
35  unique insect species and  21  unique plant species


Information on PD input data
Are all insect species of coocc dataset in insect tree:  TRUE 

Are all plant species of coocc dataset in plant tree:  TRUE 


Information on FD input data
Number of insect species in coocc dataset:  31 
Number of insect species in trait matrix:  31 
Are insect species in coocc and trait matrix identical?  TRUE 

Number of plant species in coocc dataset:  17 
Number of plant species in trait matrix:  17 
Are plant species in coocc and trait matrix identical?  TRUE 


# Alpha network diversity using iNext.link

## Taxonomic network diversity (TD)
```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)

butterfly.iNEXT.TD = iNEXT.link(data = out$cooccTD, diversity = 'TD', 
                          q = c(0),nboot = 30,knots=100)

butterfly.est.TD = estimateD.link(out$cooccTD, 
                                  q = c(0), 
                                  base = "coverage",
                                  level = seq(0,1,0.05),
                                  nboot = 30)

butterfly.plot.TD = butterfly.iNEXT.TD
butterfly.plot.TD$TDiNextEst$coverage_based = rbind(
      butterfly.iNEXT.TD$TDiNextEst$coverage_based, 
      butterfly.est.TD %>% dplyr::select(-"s.e.") %>%
        dplyr::filter(SC==0.7))


butterfly.plot.TD$TDiNextEst$coverage_based %<>% filter(SC<=0.7)

ggiNEXT.TD = ggiNEXT3D(butterfly.plot.TD, type=3,facet.var = "None",color.var ="Assemblage")

butterfly.cov.TD = ggiNEXT.TD + 
  scale_colour_manual(values = c('blue', 'red','green')) +
  scale_fill_manual(values = c('blue', 'red','green')) + 
  ggtitle("(a) Taxonomic network diversity") + ylab("Taxonomic network diversity") + 
  theme(legend.position = "bottom", plot.title = element_text(color = "blue", size = 25)) + 
  coord_cartesian(xlim = c(0.3,0.7));butterfly.cov.TD 
```



##  Phylogenetic network diversity (PD)
1 error source: tidytree
https://support.bioconductor.org/p/9153297/#9153321

solution:
if(!require("tidytree", quietly=TRUE))
  devtools::install_version("tidytree", version = "0.4.2")
  
```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)

butterfly.iNEXT.PD = iNEXT.link(data = out$cooccPD, diversity = 'PD', 
                           q = 0, nboot = 30, 
                          col.tree = out$iTree,
                          row.tree = out$pTree)

butterfly.est.PD = estimateD.link(out$cooccPD, diversity = "PD",
                            q = 0, base = "coverage", 
                            level = seq(0,1,0.05), 
                            nboot = 30,
                            col.tree = out$iTree,
                            row.tree = out$pTree)

butterfly.plot.PD = butterfly.iNEXT.PD

butterfly.plot.PD$PDiNextEst$coverage_based = rbind(butterfly.iNEXT.PD$PDiNextEst$coverage_based,
        butterfly.est.PD %>% select(-"s.e.") %>% dplyr::filter(SC==0.7))


butterfly.plot.PD$PDiNextEst$coverage_based %<>% filter(SC<=0.7)

ggiNEXT.PD = ggiNEXT3D(butterfly.plot.PD, type=3,facet.var = "None",color.var ="Assemblage")

butterfly.cov.PD = ggiNEXT.PD + 
  scale_colour_manual(values = c('blue', 'red','green')) +
  scale_fill_manual(values = c('blue', 'red','green')) + 
  ggtitle("(b) Phylogenetic network diversity") + ylab("Phylogenetic network diversity") + 
  theme(legend.position = "bottom", plot.title = element_text(color = "blue", size = 25)) + 
  coord_cartesian(xlim = c(0.3,0.7));butterfly.cov.PD
```

##Functional network diversity (FD)

```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)

butterfly.iNEXT.FD = iNEXT.link(data = out$cooccFD, diversity = 'FD', q = 0, nboot = 30, 
                          col.distM = out$iTraits.gwd,
                          row.distM = out$pTraits.gwd)

butterfly.est.FD = estimateD.link(out$cooccFD, diversity = "FD", q = 0, base = "coverage", 
                          level = seq(0,1,0.05),
                          nboot = 30, 
                          col.distM = out$iTraits.gwd,
                          row.distM = out$pTraits.gwd)

butterfly.plot.FD = butterfly.iNEXT.FD 

butterfly.plot.FD$FDiNextEst$coverage_based = rbind(butterfly.iNEXT.FD$FDiNextEst$coverage_based,
        butterfly.est.FD %>% select(-"s.e.") %>% dplyr::filter(SC==0.7))


butterfly.plot.FD$FDiNextEst$coverage_based %<>% filter(SC<=0.7)

ggiNEXT.FD = ggiNEXT3D(butterfly.plot.FD, type=3,facet.var = "None",color.var ="Assemblage")

butterfly.cov.FD = ggiNEXT.FD + 
  scale_colour_manual(values = c('blue', 'red','green')) +
  scale_fill_manual(values = c('blue', 'red','green')) + 
  ggtitle("(c) Functional network diversity") + ylab("Functional network diversity") +
  theme(plot.title = element_text(color = "blue", size = 25)) + 
  coord_cartesian(xlim = c(0.3,0.7))
```





# Save results
```{r}
save(out,
  butterfly.iNEXT.TD,
  butterfly.est.TD,
  butterfly.cov.TD,
  butterfly.iNEXT.PD,
  butterfly.est.PD,
  butterfly.cov.PD,
  butterfly.iNEXT.FD,
  butterfly.est.FD,
  butterfly.cov.FD,
  file="results/Q2_butterfly_iNext.link.RData"
)
```




