---
title: "Probabilites of the influence of grazing and environment on insect diversity"
author: "Bernd Panassiti"
date: 'created: 07.06.2023, last modified: `r format(Sys.Date(), format="%d.%m.%Y")`'
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir='../')                     # definining working directory; or normalizePath('../')
opts_chunk$set(fig.align='center',                # aligns all figures
                echo=TRUE,                        # shows r-code
                message=FALSE,                    # suppresses library outputs
                warnings=FALSE,                   # suppresses library outputs
                tidy=TRUE,  # prevents the source code from running off a pdf page
                dev='pdf')                        # pdf device
```



# Loading of packages and data
```{r loading_data, include=FALSE}
#Install/load pacman
if(!require(pacman)){install.packages("pacman");require(pacman)}
#Install packages
p_load(tidyverse,magrittr,broom.mixed,
       posterior,ggdist,tidybayes,pryr,bayesplot,
       emmeans,broom, broom.mixed,
       posterior,brms,bayesplot)

source("r-code/00_functions.R")

load("results/modelResultsSEM.RData")
```




# Hypothesis

Probabilities are calculated based on SEM results using defined hypotheses.


http://mjskay.github.io/tidybayes/

early < 0
Post.Prob: The latter indicates the posterior probability that the parameter of interest is smaller than zero (> 0). (More accurately, the proportion of samples from the posterior that are smaller than zero.)


Evid.Ratio: ratio of the hypothesis (Post.Prob)and its complement (the ratio of early > 0 and early < 0). 

https://mspeekenbrink.github.io/sdam-r-companion/bayesian-hypothesis-testing-with-bayes-factors.html
https://discourse.mc-stan.org/t/hypothesis-test-brms/28226/6


```{r}
fit = modelResultsTDVegetationManagement[[1]]


conditional_effects(fit, effects = "surveyPeriod:grazingTime")

# directional hypothesis that early is lower than control at the level of survey period 1

Q1 = "beeTDq0_surveyPeriod1:grazingTimeearly < beeTDq0_surveyPeriod1:grazingTimelate"
Q2 = "beeTDq0_surveyPeriod2:grazingTimeearly < beeTDq0_surveyPeriod2:grazingTimelate"
Q3 = "((beeTDq0_surveyPeriod1:grazingTimeearly*0.5)+(beeTDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q4 = "((beeTDq0_surveyPeriod2:grazingTimeearly*0.5)+(beeTDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q5 = "nInflorescenceCoocc_surveyPeriod1:grazingTimeearly < nInflorescenceCoocc_surveyPeriod1:grazingTimelate"
Q6 = "nInflorescenceCoocc_surveyPeriod2:grazingTimeearly > nInflorescenceCoocc_surveyPeriod2:grazingTimelate"
Q7 = "((nInflorescenceCoocc_surveyPeriod1:grazingTimeearly*0.5)+(nInflorescenceCoocc_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q8 = "((nInflorescenceCoocc_surveyPeriod2:grazingTimeearly*0.5)+(nInflorescenceCoocc_surveyPeriod2:grazingTimelate*0.5)) < 0"
hyp <- hypothesis(fit, c(Q1,Q2,Q3,Q4,Q5,Q6,Q6,Q7,Q8));hyp
```

Hypothesis Tests for class b:
                Hypothesis Estimate Est.Error CI.Lower CI.Upper Evid.Ratio Post.Prob Star
1 (beeTDq0_surveyPe... > 0    -0.64      0.90    -2.11     0.84       0.31      0.23     
2 (beeTDq0_surveyPe... > 0     1.37      0.82     0.02     2.71      20.01      0.95    *
3 (((beeTDq0_survey... > 0    -0.07      0.73    -1.25     1.13       0.86      0.46     
4 (((beeTDq0_survey... > 0     1.33      0.69     0.21     2.47      36.31      0.97    *
5 (nInflorescenceCo... < 0     0.33      0.48    -0.46     1.11       0.31      0.24     
6 (nInflorescenceCo... < 0     0.52      0.46    -0.22     1.28       0.15      0.13     

'CI': 90%-CI for one-sided and 95%-CI for two-sided hypotheses.
'*': For one-sided hypotheses, the posterior probability exceeds 95%;
for two-sided hypotheses, the value tested against lies outside the 95%-CI.
Posterior probabilities of point hypotheses assume equal prior probabilities.





## Define different alphas

```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)
alpha = 0.1
#alpha = 0.05
```

###Bees and butterflies
```{r}
# Q1-Q18 same for bees and butterflies
Q1 = "nInflorescenceCoocc_surveyPeriod1:grazingTimeearly > 0"
Q2 = "nInflorescenceCoocc_surveyPeriod2:grazingTimeearly > 0"
Q3 = "nInflorescenceCoocc_surveyPeriod1:grazingTimeearly < 0"
Q4 = "nInflorescenceCoocc_surveyPeriod2:grazingTimeearly < 0"

Q5 = "nInflorescenceCoocc_surveyPeriod1:grazingTimelate > 0"
Q6 = "nInflorescenceCoocc_surveyPeriod2:grazingTimelate > 0"
Q7 = "nInflorescenceCoocc_surveyPeriod1:grazingTimelate < 0"
Q8 = "nInflorescenceCoocc_surveyPeriod2:grazingTimelate < 0"

Q9 = "nInflorescenceCoocc_surveyPeriod1:grazingTimeearly > nInflorescenceCoocc_surveyPeriod1:grazingTimelate"
Q10 = "nInflorescenceCoocc_surveyPeriod2:grazingTimeearly > nInflorescenceCoocc_surveyPeriod2:grazingTimelate"
Q11 = "((nInflorescenceCoocc_surveyPeriod1:grazingTimeearly*0.5)+(nInflorescenceCoocc_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q12 = "((nInflorescenceCoocc_surveyPeriod2:grazingTimeearly*0.5)+(nInflorescenceCoocc_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q13 = "nInflorescenceCoocc_surveyPeriod1:grazingTimeearly < nInflorescenceCoocc_surveyPeriod1:grazingTimelate"
Q14 = "nInflorescenceCoocc_surveyPeriod2:grazingTimeearly < nInflorescenceCoocc_surveyPeriod2:grazingTimelate"
Q15 = "((nInflorescenceCoocc_surveyPeriod1:grazingTimeearly*0.5)+(nInflorescenceCoocc_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q16 = "((nInflorescenceCoocc_surveyPeriod2:grazingTimeearly*0.5)+(nInflorescenceCoocc_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q17 =  "nInflorescenceCoocc_elevationScaled > 0"
Q18 = "nInflorescenceCoocc_elevationScaled < 0"


Q19 = "beeTDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "beeTDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "beeTDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "beeTDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "beeTDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "beeTDq0_surveyPeriod2:grazingTimelate > 0"
Q25= "beeTDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "beeTDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "beeTDq0_surveyPeriod1:grazingTimeearly > beeTDq0_surveyPeriod1:grazingTimelate"
Q28 = "beeTDq0_surveyPeriod2:grazingTimeearly > beeTDq0_surveyPeriod2:grazingTimelate"
Q29 = "((beeTDq0_surveyPeriod1:grazingTimeearly*0.5)+(beeTDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((beeTDq0_surveyPeriod2:grazingTimeearly*0.5)+(beeTDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "beeTDq0_surveyPeriod1:grazingTimeearly < beeTDq0_surveyPeriod1:grazingTimelate"
Q32 = "beeTDq0_surveyPeriod2:grazingTimeearly < beeTDq0_surveyPeriod2:grazingTimelate"
Q33 = "((beeTDq0_surveyPeriod1:grazingTimeearly*0.5)+(beeTDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((beeTDq0_surveyPeriod2:grazingTimeearly*0.5)+(beeTDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "beeTDq0_elevationScaled > 0"
Q36 = "beeTDq0_elevationScaled < 0"
Q37 = "beeTDq0_nInflorescenceCoocc > 0"
hypTDbee  = hypothesis(modelResultsTDVegetationManagement[[1]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)


Q19 = "beePDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "beePDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "beePDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "beePDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "beePDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "beePDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "beePDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "beePDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "beePDq0_surveyPeriod1:grazingTimeearly > beePDq0_surveyPeriod1:grazingTimelate"
Q28 = "beePDq0_surveyPeriod2:grazingTimeearly > beePDq0_surveyPeriod2:grazingTimelate"
Q29 = "((beePDq0_surveyPeriod1:grazingTimeearly*0.5)+(beePDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((beePDq0_surveyPeriod2:grazingTimeearly*0.5)+(beePDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "beePDq0_surveyPeriod1:grazingTimeearly < beePDq0_surveyPeriod1:grazingTimelate"
Q32 = "beePDq0_surveyPeriod2:grazingTimeearly < beePDq0_surveyPeriod2:grazingTimelate"
Q33 = "((beePDq0_surveyPeriod1:grazingTimeearly*0.5)+(beePDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((beePDq0_surveyPeriod2:grazingTimeearly*0.5)+(beePDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "beePDq0_elevationScaled > 0"
Q36 = "beePDq0_elevationScaled < 0"
Q37 = "beePDq0_nInflorescenceCoocc >0"
hypPDbee  = hypothesis(modelResultsPDVegetationManagement[[1]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)


Q19 = "beeFDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "beeFDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "beeFDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "beeFDq0_surveyPeriod2:grazingTimeearly < 0"


Q23 = "beeFDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "beeFDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "beeFDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "beeFDq0_surveyPeriod2:grazingTimelate < 0"


Q27 = "beeFDq0_surveyPeriod1:grazingTimeearly > beeFDq0_surveyPeriod1:grazingTimelate"
Q28 = "beeFDq0_surveyPeriod2:grazingTimeearly > beeFDq0_surveyPeriod2:grazingTimelate"
Q29 = "((beeFDq0_surveyPeriod1:grazingTimeearly*0.5)+(beeFDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((beeFDq0_surveyPeriod2:grazingTimeearly*0.5)+(beeFDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "beeFDq0_surveyPeriod1:grazingTimeearly < beeFDq0_surveyPeriod1:grazingTimelate"
Q32 = "beeFDq0_surveyPeriod2:grazingTimeearly < beeFDq0_surveyPeriod2:grazingTimelate"
Q33 = "((beeFDq0_surveyPeriod1:grazingTimeearly*0.5)+(beeFDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((beeFDq0_surveyPeriod2:grazingTimeearly*0.5)+(beeFDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "beeFDq0_elevationScaled > 0"
Q36 = "beeFDq0_elevationScaled < 0"
Q37 = "beeFDq0_nInflorescenceCoocc >0"
hypFDbee  = hypothesis(modelResultsFDVegetationManagement[[1]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)


# butterfly
Q19 = "butterflyTDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "butterflyTDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "butterflyTDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "butterflyTDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "butterflyTDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "butterflyTDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "butterflyTDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "butterflyTDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "butterflyTDq0_surveyPeriod1:grazingTimeearly > butterflyTDq0_surveyPeriod1:grazingTimelate"
Q28 = "butterflyTDq0_surveyPeriod2:grazingTimeearly > butterflyTDq0_surveyPeriod2:grazingTimelate"
Q29= "((butterflyTDq0_surveyPeriod1:grazingTimeearly*0.5)+(butterflyTDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((butterflyTDq0_surveyPeriod2:grazingTimeearly*0.5)+(butterflyTDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "butterflyTDq0_surveyPeriod1:grazingTimeearly < butterflyTDq0_surveyPeriod1:grazingTimelate"
Q32 = "butterflyTDq0_surveyPeriod2:grazingTimeearly < butterflyTDq0_surveyPeriod2:grazingTimelate"
Q33 = "((butterflyTDq0_surveyPeriod1:grazingTimeearly*0.5)+(butterflyTDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((butterflyTDq0_surveyPeriod2:grazingTimeearly*0.5)+(butterflyTDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "butterflyTDq0_elevationScaled > 0"
Q36 = "butterflyTDq0_elevationScaled < 0"
Q37 = "butterflyTDq0_nInflorescenceCoocc > 0"
hypTDbutterfly = hypothesis(modelResultsTDVegetationManagement[[2]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha) 

Q19 = "butterflyPDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "butterflyPDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "butterflyPDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "butterflyPDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "butterflyPDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "butterflyPDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "butterflyPDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "butterflyPDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "butterflyPDq0_surveyPeriod1:grazingTimeearly > butterflyPDq0_surveyPeriod1:grazingTimelate"
Q28 = "butterflyPDq0_surveyPeriod2:grazingTimeearly > butterflyPDq0_surveyPeriod2:grazingTimelate"
Q29 = "((butterflyPDq0_surveyPeriod1:grazingTimeearly*0.5)+(butterflyPDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((butterflyPDq0_surveyPeriod2:grazingTimeearly*0.5)+(butterflyPDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "butterflyPDq0_surveyPeriod1:grazingTimeearly < butterflyPDq0_surveyPeriod1:grazingTimelate"
Q32 = "butterflyPDq0_surveyPeriod2:grazingTimeearly < butterflyPDq0_surveyPeriod2:grazingTimelate"
Q33 = "((butterflyPDq0_surveyPeriod1:grazingTimeearly*0.5)+(butterflyPDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((butterflyPDq0_surveyPeriod2:grazingTimeearly*0.5)+(butterflyPDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "butterflyPDq0_elevationScaled > 0"
Q36 = "butterflyPDq0_elevationScaled < 0"
Q37 = "butterflyPDq0_nInflorescenceCoocc >0"
hypPDbutterfly   = hypothesis(modelResultsPDVegetationManagement[[2]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)
Q19 = "butterflyFDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "butterflyFDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "butterflyFDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "butterflyFDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "butterflyFDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "butterflyFDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "butterflyFDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "butterflyFDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "butterflyFDq0_surveyPeriod1:grazingTimeearly > butterflyFDq0_surveyPeriod1:grazingTimelate"
Q28 = "butterflyFDq0_surveyPeriod2:grazingTimeearly > butterflyFDq0_surveyPeriod2:grazingTimelate"
Q29 = "((butterflyFDq0_surveyPeriod1:grazingTimeearly*0.5)+(butterflyFDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((butterflyFDq0_surveyPeriod2:grazingTimeearly*0.5)+(butterflyFDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "butterflyFDq0_surveyPeriod1:grazingTimeearly < butterflyFDq0_surveyPeriod1:grazingTimelate"
Q32 = "butterflyFDq0_surveyPeriod2:grazingTimeearly < butterflyFDq0_surveyPeriod2:grazingTimelate"
Q33 = "((butterflyFDq0_surveyPeriod1:grazingTimeearly*0.5)+(butterflyFDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((butterflyFDq0_surveyPeriod2:grazingTimeearly*0.5)+(butterflyFDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "butterflyFDq0_elevationScaled > 0"
Q36 = "butterflyFDq0_elevationScaled < 0"
Q37 = "butterflyFDq0_nInflorescenceCoocc >0"
hypFDbutterfly   = hypothesis(modelResultsFDVegetationManagement[[2]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha) 
```

### Planthopper
#### Planthopper - Plant species richness
```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)

Q1 = "nPlantSpecies_surveyPeriod1:grazingTimeearly > 0"
Q2 = "nPlantSpecies_surveyPeriod2:grazingTimeearly > 0"
Q3 = "nPlantSpecies_surveyPeriod1:grazingTimeearly < 0"
Q4 = "nPlantSpecies_surveyPeriod2:grazingTimeearly < 0"

Q5 = "nPlantSpecies_surveyPeriod1:grazingTimelate > 0"
Q6 = "nPlantSpecies_surveyPeriod2:grazingTimelate > 0"
Q7 = "nPlantSpecies_surveyPeriod1:grazingTimelate < 0"
Q8 = "nPlantSpecies_surveyPeriod2:grazingTimelate < 0"

Q9 = "nPlantSpecies_surveyPeriod1:grazingTimeearly > nPlantSpecies_surveyPeriod1:grazingTimelate"
Q10 = "nPlantSpecies_surveyPeriod2:grazingTimeearly > nPlantSpecies_surveyPeriod2:grazingTimelate"
Q11 = "((nPlantSpecies_surveyPeriod1:grazingTimeearly*0.5)+(nPlantSpecies_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q12 = "((nPlantSpecies_surveyPeriod2:grazingTimeearly*0.5)+(nPlantSpecies_surveyPeriod2:grazingTimelate*0.5)) > 0"

Q13 = "nPlantSpecies_surveyPeriod1:grazingTimeearly < nPlantSpecies_surveyPeriod1:grazingTimelate"
Q14 = "nPlantSpecies_surveyPeriod2:grazingTimeearly < nPlantSpecies_surveyPeriod2:grazingTimelate"
Q15 = "((nPlantSpecies_surveyPeriod1:grazingTimeearly*0.5)+(nPlantSpecies_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q16 = "((nPlantSpecies_surveyPeriod2:grazingTimeearly*0.5)+(nPlantSpecies_surveyPeriod2:grazingTimelate*0.5)) < 0"

Q17 =  "nPlantSpecies_elevationScaled > 0"
Q18 = "nPlantSpecies_elevationScaled < 0"


Q19 = "planthopperTDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperTDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperTDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperTDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperTDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperTDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperTDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperTDq0_surveyPeriod2:grazingTimelate < 0"


Q27  = "planthopperTDq0_surveyPeriod1:grazingTimeearly > planthopperTDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperTDq0_surveyPeriod2:grazingTimeearly > planthopperTDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperTDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperTDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperTDq0_surveyPeriod1:grazingTimeearly < planthopperTDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperTDq0_surveyPeriod2:grazingTimeearly < planthopperTDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperTDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperTDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperTDq0_elevationScaled > 0"
Q36 = "planthopperTDq0_elevationScaled < 0"
Q37 = "planthopperTDq0_nPlantSpecies > 0"
hypTDplanthopper = hypothesis(modelResultsTDVegetationManagement[[3]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)

Q19 = "planthopperPDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperPDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperPDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperPDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperPDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperPDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperPDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperPDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "planthopperPDq0_surveyPeriod1:grazingTimeearly > planthopperPDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperPDq0_surveyPeriod2:grazingTimeearly > planthopperPDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperPDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperPDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperPDq0_surveyPeriod1:grazingTimeearly < planthopperPDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperPDq0_surveyPeriod2:grazingTimeearly < planthopperPDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperPDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperPDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperPDq0_elevationScaled > 0"
Q36 = "planthopperPDq0_elevationScaled < 0"
Q37 = "planthopperPDq0_nPlantSpecies > 0"
hypPDplanthopper = hypothesis(modelResultsPDVegetationManagement[[3]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)


Q19 = "planthopperFDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperFDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperFDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperFDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperFDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperFDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperFDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperFDq0_surveyPeriod2:grazingTimelate < 0"


Q27 = "planthopperFDq0_surveyPeriod1:grazingTimeearly > planthopperFDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperFDq0_surveyPeriod2:grazingTimeearly > planthopperFDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperFDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperFDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperFDq0_surveyPeriod1:grazingTimeearly < planthopperFDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperFDq0_surveyPeriod2:grazingTimeearly < planthopperFDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperFDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperFDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperFDq0_elevationScaled > 0"
Q36 = "planthopperFDq0_elevationScaled < 0"
Q37 = "planthopperFDq0_nPlantSpecies > 0"
hypFDplanthopper = hypothesis(modelResultsFDVegetationManagement[[3]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)
```

####  Planthopper - Height
```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)

Q1 = "height_surveyPeriod1:grazingTimeearly > 0"
Q2 = "height_surveyPeriod2:grazingTimeearly > 0"
Q3 = "height_surveyPeriod1:grazingTimeearly < 0"
Q4 = "height_surveyPeriod2:grazingTimeearly < 0"

Q5 = "height_surveyPeriod1:grazingTimelate > 0"
Q6 = "height_surveyPeriod2:grazingTimelate > 0"
Q7 = "height_surveyPeriod1:grazingTimelate < 0"
Q8 = "height_surveyPeriod2:grazingTimelate < 0"

Q9 = "height_surveyPeriod1:grazingTimeearly > height_surveyPeriod1:grazingTimelate"
Q10 = "height_surveyPeriod2:grazingTimeearly > height_surveyPeriod2:grazingTimelate"
Q11 = "((height_surveyPeriod1:grazingTimeearly*0.5)+(height_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q12 = "((height_surveyPeriod2:grazingTimeearly*0.5)+(height_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q13 = "height_surveyPeriod1:grazingTimeearly < height_surveyPeriod1:grazingTimelate"
Q14 = "height_surveyPeriod2:grazingTimeearly < height_surveyPeriod2:grazingTimelate"
Q15 = "((height_surveyPeriod1:grazingTimeearly*0.5)+(height_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q16 = "((height_surveyPeriod2:grazingTimeearly*0.5)+(height_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q17 =  "height_elevationScaled > 0"
Q18 = "height_elevationScaled < 0"


Q19 = "planthopperTDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperTDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperTDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperTDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperTDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperTDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperTDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperTDq0_surveyPeriod2:grazingTimelate < 0"

Q27  = "planthopperTDq0_surveyPeriod1:grazingTimeearly > planthopperTDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperTDq0_surveyPeriod2:grazingTimeearly > planthopperTDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperTDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperTDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperTDq0_surveyPeriod1:grazingTimeearly < planthopperTDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperTDq0_surveyPeriod2:grazingTimeearly < planthopperTDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperTDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperTDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperTDq0_elevationScaled > 0"
Q36 = "planthopperTDq0_elevationScaled < 0"
Q37 = "planthopperTDq0_height > 0"
hypTDplanthopper2 = hypothesis(modelResultsTDVegetationManagement[[4]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)

Q19 = "planthopperPDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperPDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperPDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperPDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperPDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperPDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperPDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperPDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "planthopperPDq0_surveyPeriod1:grazingTimeearly > planthopperPDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperPDq0_surveyPeriod2:grazingTimeearly > planthopperPDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperPDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperPDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperPDq0_surveyPeriod1:grazingTimeearly < planthopperPDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperPDq0_surveyPeriod2:grazingTimeearly < planthopperPDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperPDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperPDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperPDq0_elevationScaled > 0"
Q36 = "planthopperPDq0_elevationScaled < 0"
Q37 = "planthopperPDq0_height > 0"
hypPDplanthopper2 = hypothesis(modelResultsPDVegetationManagement[[4]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)


Q19 = "planthopperFDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperFDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperFDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperFDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperFDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperFDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperFDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperFDq0_surveyPeriod2:grazingTimelate < 0"


Q27 = "planthopperFDq0_surveyPeriod1:grazingTimeearly > planthopperFDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperFDq0_surveyPeriod2:grazingTimeearly > planthopperFDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperFDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperFDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperFDq0_surveyPeriod1:grazingTimeearly < planthopperFDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperFDq0_surveyPeriod2:grazingTimeearly < planthopperFDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperFDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperFDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperFDq0_elevationScaled > 0"
Q36 = "planthopperFDq0_elevationScaled < 0"
Q37 = "planthopperFDq0_height > 0"
hypFDplanthopper2 = hypothesis(modelResultsFDVegetationManagement[[4]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)
```

####  Planthopper - Biomass
```{r}
rm(.Random.seed, envir=globalenv())
set.seed(2023)


Q1 = "biomass_surveyPeriod1:grazingTimeearly > 0"
Q2 = "biomass_surveyPeriod2:grazingTimeearly > 0"
Q3 = "biomass_surveyPeriod1:grazingTimeearly < 0"
Q4 = "biomass_surveyPeriod2:grazingTimeearly < 0"

Q5 = "biomass_surveyPeriod1:grazingTimelate > 0"
Q6 = "biomass_surveyPeriod2:grazingTimelate > 0"
Q7 = "biomass_surveyPeriod1:grazingTimelate < 0"
Q8 = "biomass_surveyPeriod2:grazingTimelate < 0"



Q9 = "biomass_surveyPeriod1:grazingTimeearly > biomass_surveyPeriod1:grazingTimelate"
Q10 = "biomass_surveyPeriod2:grazingTimeearly > biomass_surveyPeriod2:grazingTimelate"
Q11 = "((biomass_surveyPeriod1:grazingTimeearly*0.5)+(biomass_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q12 = "((biomass_surveyPeriod2:grazingTimeearly*0.5)+(biomass_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q13 = "biomass_surveyPeriod1:grazingTimeearly < biomass_surveyPeriod1:grazingTimelate"
Q14 = "biomass_surveyPeriod2:grazingTimeearly < biomass_surveyPeriod2:grazingTimelate"
Q15 = "((biomass_surveyPeriod1:grazingTimeearly*0.5)+(biomass_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q16 = "((biomass_surveyPeriod2:grazingTimeearly*0.5)+(biomass_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q17 =  "biomass_elevationScaled > 0"
Q18 = "biomass_elevationScaled < 0"


Q19 = "planthopperTDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperTDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperTDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperTDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperTDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperTDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperTDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperTDq0_surveyPeriod2:grazingTimelate < 0"

Q27  = "planthopperTDq0_surveyPeriod1:grazingTimeearly > planthopperTDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperTDq0_surveyPeriod2:grazingTimeearly > planthopperTDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperTDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperTDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperTDq0_surveyPeriod1:grazingTimeearly < planthopperTDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperTDq0_surveyPeriod2:grazingTimeearly < planthopperTDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperTDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperTDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperTDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperTDq0_elevationScaled > 0"
Q36 = "planthopperTDq0_elevationScaled < 0"
Q37 = "planthopperTDq0_biomass > 0"
hypTDplanthopper3 = hypothesis(modelResultsTDVegetationManagement[[5]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)


Q19 = "planthopperPDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperPDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperPDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperPDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperPDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperPDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperPDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperPDq0_surveyPeriod2:grazingTimelate < 0"

Q27 = "planthopperPDq0_surveyPeriod1:grazingTimeearly > planthopperPDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperPDq0_surveyPeriod2:grazingTimeearly > planthopperPDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperPDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperPDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperPDq0_surveyPeriod1:grazingTimeearly < planthopperPDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperPDq0_surveyPeriod2:grazingTimeearly < planthopperPDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperPDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperPDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperPDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperPDq0_elevationScaled > 0"
Q36 = "planthopperPDq0_elevationScaled < 0"
Q37 = "planthopperPDq0_biomass > 0"
hypPDplanthopper3 = hypothesis(modelResultsPDVegetationManagement[[5]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)

Q19 = "planthopperFDq0_surveyPeriod1:grazingTimeearly > 0"
Q20 = "planthopperFDq0_surveyPeriod2:grazingTimeearly > 0"
Q21 = "planthopperFDq0_surveyPeriod1:grazingTimeearly < 0"
Q22 = "planthopperFDq0_surveyPeriod2:grazingTimeearly < 0"

Q23 = "planthopperFDq0_surveyPeriod1:grazingTimelate > 0"
Q24 = "planthopperFDq0_surveyPeriod2:grazingTimelate > 0"
Q25 = "planthopperFDq0_surveyPeriod1:grazingTimelate < 0"
Q26 = "planthopperFDq0_surveyPeriod2:grazingTimelate < 0"


Q27 = "planthopperFDq0_surveyPeriod1:grazingTimeearly > planthopperFDq0_surveyPeriod1:grazingTimelate"
Q28 = "planthopperFDq0_surveyPeriod2:grazingTimeearly > planthopperFDq0_surveyPeriod2:grazingTimelate"
Q29 = "((planthopperFDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod1:grazingTimelate*0.5)) > 0"
Q30 = "((planthopperFDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod2:grazingTimelate*0.5)) > 0"
Q31 = "planthopperFDq0_surveyPeriod1:grazingTimeearly < planthopperFDq0_surveyPeriod1:grazingTimelate"
Q32 = "planthopperFDq0_surveyPeriod2:grazingTimeearly < planthopperFDq0_surveyPeriod2:grazingTimelate"
Q33 = "((planthopperFDq0_surveyPeriod1:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod1:grazingTimelate*0.5)) < 0"
Q34 = "((planthopperFDq0_surveyPeriod2:grazingTimeearly*0.5)+(planthopperFDq0_surveyPeriod2:grazingTimelate*0.5)) < 0"
Q35 = "planthopperFDq0_elevationScaled > 0"
Q36 = "planthopperFDq0_elevationScaled < 0"
Q37 = "planthopperFDq0_biomass > 0"
hypFDplanthopper3 = hypothesis(modelResultsFDVegetationManagement[[5]],c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,
                                                                  Q11,Q12,Q13,Q14,Q15,Q16,Q17,Q18,
                                                                  Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,
                                                                  Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,
                                                                  Q35,Q36,Q37),alpha=alpha)
```

### Combine hypothesis
```{r}
nHypotheses = 37
hypTDbee$hypothesis$diversity =rep("TD",nHypotheses)
hypTDbee$hypothesis$group =rep("bee",nHypotheses)
hypTDbutterfly$hypothesis$diversity =rep("TD",nHypotheses)
hypTDbutterfly$hypothesis$group =rep("butterfly",nHypotheses)
hypTDplanthopper$hypothesis$diversity =rep("TD",nHypotheses)
hypTDplanthopper$hypothesis$group =rep("planthopper",nHypotheses)
hypTDplanthopper2$hypothesis$diversity =rep("TD",nHypotheses)
hypTDplanthopper2$hypothesis$group =rep("planthopper2",nHypotheses)
hypTDplanthopper3$hypothesis$diversity =rep("TD",nHypotheses)
hypTDplanthopper3$hypothesis$group =rep("planthopper3",nHypotheses)

hypPDbee$hypothesis$diversity =rep("PD",nHypotheses)
hypPDbee$hypothesis$group =rep("bee",nHypotheses)
hypPDbutterfly$hypothesis$diversity =rep("PD",nHypotheses)
hypPDbutterfly$hypothesis$group =rep("butterfly",nHypotheses)
hypPDplanthopper$hypothesis$diversity =rep("PD",nHypotheses)
hypPDplanthopper$hypothesis$group =rep("planthopper",nHypotheses)
hypPDplanthopper2$hypothesis$diversity =rep("PD",nHypotheses)
hypPDplanthopper2$hypothesis$group =rep("planthopper2",nHypotheses)
hypPDplanthopper3$hypothesis$diversity =rep("PD",nHypotheses)
hypPDplanthopper3$hypothesis$group =rep("planthopper3",nHypotheses)

hypFDbee$hypothesis$diversity =rep("FD",nHypotheses)
hypFDbee$hypothesis$group =rep("bee",nHypotheses)
hypFDbutterfly$hypothesis$diversity =rep("FD",nHypotheses)
hypFDbutterfly$hypothesis$group =rep("butterfly",nHypotheses)
hypFDplanthopper$hypothesis$diversity =rep("FD",nHypotheses)
hypFDplanthopper$hypothesis$group =rep("planthopper",nHypotheses)
hypFDplanthopper2$hypothesis$diversity =rep("FD",nHypotheses)
hypFDplanthopper2$hypothesis$group =rep("planthopper2",nHypotheses)
hypFDplanthopper3$hypothesis$diversity =rep("FD",nHypotheses)
hypFDplanthopper3$hypothesis$group =rep("planthopper3",nHypotheses)

hypothesesResults = rbind(
hypTDbee$hypothesis,
hypTDbutterfly$hypothesis,
hypTDplanthopper$hypothesis,
hypTDplanthopper2$hypothesis,
hypTDplanthopper3$hypothesis,

hypPDbee$hypothesis,
hypPDbutterfly$hypothesis,
hypPDplanthopper$hypothesis,
hypPDplanthopper2$hypothesis,
hypPDplanthopper3$hypothesis,

hypFDbee$hypothesis,
hypFDbutterfly$hypothesis,
hypFDplanthopper$hypothesis,
hypFDplanthopper2$hypothesis,
hypFDplanthopper3$hypothesis)


# renaming
hypothesesResults$model = rep(c(rep("p",18),rep("i",19)),15)



hypothesesResults.0.9 = hypothesesResults # alpha = 0.1
#hypothesesResults.0.95 = hypothesesResults # alpha = 0.05
```



```{r}
df1 = hypothesesResults.0.9 %>% rename(alpha_0.9 = Star)
df2 = hypothesesResults.0.95 %>% rename(alpha_0.95 = Star) %>% dplyr::select(Hypothesis,diversity,group,model,Post.Prob,alpha_0.95)
df = merge(df1,df2,by=c("Hypothesis","diversity","group","model","Post.Prob"),all.x=T)


df$diversity = as.factor(df$diversity)
df$diversity <- factor(df$diversity, levels = c("TD","PD","FD"))

dfN = df

# renaming
dfN$Hypothesis_fullname = df$Hypothesis
dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimelate) > 0",dfN$Hypothesis_fullname))] = "SP1: late > 0"
dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimelate) > 0",dfN$Hypothesis_fullname))] = "SP2: late > 0"
dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimelate) < 0",dfN$Hypothesis_fullname))] = "SP1: late < 0"
dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimelate) < 0",dfN$Hypothesis_fullname))] = "SP2: late < 0"

dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimeearly) > 0",dfN$Hypothesis_fullname))] = "SP1: early > 0"
dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimeearly) > 0",dfN$Hypothesis_fullname))] = "SP2: early > 0"
dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimeearly) < 0",dfN$Hypothesis_fullname))] = "SP1: early < 0"
dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimeearly) < 0",dfN$Hypothesis_fullname))] = "SP2: early < 0"


dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimelate\\*0.5))) > 0",dfN$Hypothesis_fullname))] = 
  "SP1: grazing > control"
dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimelate\\*0.5))) > 0",dfN$Hypothesis_fullname))] = 
  "SP2: grazing > control"
dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimelate\\*0.5))) < 0",dfN$Hypothesis_fullname))] = 
  "SP1: grazing < control"
dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimelate\\*0.5))) < 0",dfN$Hypothesis_fullname))] = 
  "SP2: grazing < control"

dfN$Hypothesis[which(grepl("elevationScaled) > 0",dfN$Hypothesis_fullname))] = "elevation > 0"
dfN$Hypothesis[which(grepl("elevationScaled) < 0",dfN$Hypothesis_fullname))] = "elevation < 0"

dfN$Hypothesis[which(grepl("nInflorescenceCoocc)",dfN$Hypothesis_fullname))] = "nInflorescences > 0"
dfN$Hypothesis[which(grepl("nPlantSpecies)",dfN$Hypothesis_fullname))]       = "nPlantSpecies > 0"
dfN$Hypothesis[which(grepl("height)",dfN$Hypothesis_fullname))]              = "height > 0"
dfN$Hypothesis[which(grepl("biomass)",dfN$Hypothesis_fullname))]             = "biomass > 0"



dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimeearly)-",dfN$Hypothesis_fullname) & 
                       grepl("surveyPeriod1:grazingTimelate) > 0",dfN$Hypothesis_fullname),dfN$Hypothesis_fullname)]= "SP1: early > late"

dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimeearly)-",dfN$Hypothesis_fullname) & 
                       grepl("surveyPeriod2:grazingTimelate) > 0",dfN$Hypothesis_fullname),dfN$Hypothesis_fullname)]= "SP2: early > late"

dfN$Hypothesis[which(grepl("surveyPeriod1:grazingTimeearly)-",dfN$Hypothesis_fullname) & 
                       grepl("surveyPeriod1:grazingTimelate) < 0",dfN$Hypothesis_fullname),dfN$Hypothesis_fullname)]= "SP1: early < late"

dfN$Hypothesis[which(grepl("surveyPeriod2:grazingTimeearly)-",dfN$Hypothesis_fullname) & 
                       grepl("surveyPeriod2:grazingTimelate) < 0",dfN$Hypothesis_fullname),dfN$Hypothesis_fullname)]= "SP2: early < late"




dfN %<>% relocate(Hypothesis_fullname, .after = last_col())
hypothesesResults = dfN %>% dplyr::arrange(diversity,group,model,Hypothesis)


```


# Save model results
```{r}
openxlsx::write.xlsx(hypothesesResults,paste("results/",gsub("-"
                                                             ,".",Sys.Date()),"-Q2_Hypotheses_SEM.xlsx",sep=""))

save(hypothesesResults,
     file="results/modelResultsSEM_hypotheses.RData")
```

