---
title: "Calculation of contrasts"
author: "Bernd Panassiti"
date: 'created: 07.06.2023, last modified: `r format(Sys.Date(), format="%d.%m.%Y")`'
output:
  pdf_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir='../')                     # definining working directory; or normalizePath('../')
opts_chunk$set(fig.align='center',                # aligns all figures
                echo=TRUE,                        # shows r-code
                message=FALSE,                    # suppresses library outputs
                warnings=FALSE,                   # suppresses library outputs
                tidy=TRUE,  # prevents the source code from running off a pdf page
                dev='pdf')                        # pdf device
```




# Introduction

This script provides the R-code for the statistical analyses to evaluate the influence of grazing time on insect diversity in alpine pastures.

2 hypotheses are investigated:

1) Influence of grazing time (early, late) on insect diversity depending on survey period and year
2)


Reponse data: taxonomic, phylogenetic and functional alpha diversity of Apiformes, Papilionoidea, Auchenorrhyncha

Using iNEXT3d estimates, I assume that respones follows a Gaussian distribution


With random effect

(1 | A/B) translates to (1 | A) + (1 | A:B) where A:B simply means creating a new grouping factor with the levels of A and B pasted together:
If the user were to write (1 | g1/g2), brms will expand this to (1 | g1) + (1 | g1:g2)
https://journal.r-project.org/archive/2018/RJ-2018-017/index.html

lmer:
https://www.phonetik.uni-muenchen.de/~jmh/lehre/sem/ss18/statistikR_files/MixedModels.html

https://ourcodingclub.github.io/tutorials/mixed-models/

for model formulation of interaction of two factor variables see:
https://stackoverflow.com/questions/40729701/how-to-use-formula-in-r-to-exclude-main-effect-but-retain-interaction




# Loading of packages and data
```{r loading_data, include=FALSE}
#Install/load pacman
if(!require(pacman)){install.packages("pacman");require(pacman)}
#Install packages
p_load(tidyverse,magrittr,caret,ggplot2,DHARMa,broom.mixed,
       posterior,ggdist,tidybayes,pryr,bayesplot,ggpubr,grid,gridExtra,
       emmeans,broom, broom.mixed,
       posterior,brms,bayesplot,ggpubr,
       hrbrthemes,patchwork,# additional themes
       GGally) # ggpairs

source("r-code/00_functions.R")

load("results/modelResults.RData")
```



# Contrasts

## Examples with emmeans
### Management predictors
```{r}
emm2=emmeans::emmeans(modelResultsTDManagement[[1]], ~grazingTime * surveyPeriod)
contrast(emm2,"pairwise",by="surveyPeriod",type="response")
```
surveyPeriod = 1:
 contrast        estimate lower.HPD upper.HPD
 control - early    0.963    -0.571     2.529
 control - late     0.327    -1.220     1.890
 early - late      -0.635    -2.130     1.005

surveyPeriod = 2:
 contrast        estimate lower.HPD upper.HPD
 control - early   -0.687    -2.203     0.812
 control - late     0.486    -0.973     2.045
 early - late       1.180    -0.335     2.706

Results are averaged over the levels of: year 
Point estimate displayed: median 
HPD interval probability: 0.95 

```{r}
EMM = emmeans::emmeans(modelResultsTDManagement[[1]], ~grazingTime*surveyPeriod)
emmeans::joint_tests(EMM)


summary(pairs(EMM),by = NULL, adjust = "mvt")

modelResultsTDManagement[[1]] %>%
  emmeans( ~ grazingTime| surveyPeriod) %>%
  gather_emmeans_draws() %>%
  ggplot(aes(x = grazingTime, y = .value)) +
  geom_line(aes(group = .draw), alpha = .005) +
  stat_pointinterval() +
  facet_grid(~  surveyPeriod) +
  theme_light()
```


### Grazing vs. Control and Early vs. Late
Define contrasts
```{r}
Contrasts = list(control.vs.grazing = c(-1,1/2,1/2), # same as = c(2,-1,-1)/2
                 early.vs.late = c(0,1,-1))
```


```{r}
emm <- emmeans(modelResultsTDManagement[[1]], ~ grazingTime * surveyPeriod)
contrast(emm, Contrasts, by = "surveyPeriod")
```

surveyPeriod = 1:
 contrast           estimate lower.HPD upper.HPD
 control.vs.grazing  -0.6406    -1.971     0.716
 early.vs.late       -0.6351    -2.130     1.005

surveyPeriod = 2:
 contrast           estimate lower.HPD upper.HPD
 control.vs.grazing   0.0991    -1.219     1.405
 early.vs.late        1.1796    -0.335     2.706

Results are averaged over the levels of: year 
Point estimate displayed: median 
HPD interval probability: 0.95

## BRM:Hypothesis

https://mspeekenbrink.github.io/sdam-r-companion/bayesian-hypothesis-testing-with-bayes-factors.html
https://mvuorre.github.io/posts/2020-02-06-how-to-calculate-contrasts-from-a-fitted-brms-model/
https://groups.google.com/g/brms-users/c/oFUWA3hl6rc/m/8LJFQaHhBwAJ
https://mspeekenbrink.github.io/sdam-r-companion/bayesian-hypothesis-testing-with-bayes-factors.html

Q1) Early SP1 > Late SP1
Q2) Early SP2 > Late SP2
Q3) Early+Late SP1 < Control SP1
Q4) Early+Late SP2 < Control SP2

evidence ratio: p/(1-p); P = posterior probability

emmeans uses HPDs by default while brms uses (quantile-based) credible intervals

```{r}
Q1 = c("surveyPeriod1:grazingTimeearly > 0")
Q2 = c("surveyPeriod2:grazingTimeearly > 0")
Q3 = c("surveyPeriod1:grazingTimelate > 0")
Q4 = c("surveyPeriod2:grazingTimelate > 0")
Q5 = c("surveyPeriod1:grazingTimeearly < 0")
Q6 = c("surveyPeriod2:grazingTimeearly < 0")
Q7 = c("surveyPeriod1:grazingTimelate < 0")
Q8 = c("surveyPeriod2:grazingTimelate < 0")

Q9  = c("surveyPeriod1:grazingTimeearly > surveyPeriod1:grazingTimelate")
Q10 = c("surveyPeriod2:grazingTimeearly > surveyPeriod2:grazingTimelate")
Q11 = c("surveyPeriod1:grazingTimeearly < surveyPeriod1:grazingTimelate")
Q12 = c("surveyPeriod2:grazingTimeearly < surveyPeriod2:grazingTimelate")


Q13 = c("((surveyPeriod1:grazingTimeearly*0.5)+(surveyPeriod1:grazingTimelate*0.5)) > 0")
Q14 = c("((surveyPeriod2:grazingTimeearly*0.5)+(surveyPeriod2:grazingTimelate*0.5)) > 0")
Q15 = c("((surveyPeriod1:grazingTimeearly*0.5)+(surveyPeriod1:grazingTimelate*0.5)) < 0")
Q16 = c("((surveyPeriod2:grazingTimeearly*0.5)+(surveyPeriod2:grazingTimelate*0.5)) < 0")

Q17 = c("surveyPeriod1:nPlantSpecies > 0")
Q18 = c("surveyPeriod2:nPlantSpecies > 0")
Q19 = c("surveyPeriod1:nInflorescenceCoocc > 0")
Q20 = c("surveyPeriod2:nInflorescenceCoocc > 0")
Q21 = c("surveyPeriod1:coverHerbs > 0")
Q22 = c("surveyPeriod2:coverHerbs > 0")
Q23 = c("surveyPeriod1:nPlantSpecies < 0")
Q24 = c("surveyPeriod2:nPlantSpecies < 0")
Q25 = c("surveyPeriod1:nInflorescenceCoocc < 0")
Q26 = c("surveyPeriod2:nInflorescenceCoocc < 0")
Q27 = c("surveyPeriod1:coverHerbs < 0")
Q28 = c("surveyPeriod2:coverHerbs < 0")

Q29 = c("surveyPeriod1:height > 0")
Q30 = c("surveyPeriod2:height > 0")
Q31 = c("surveyPeriod1:biomass > 0")
Q32 = c("surveyPeriod2:biomass > 0")
Q33 = c("surveyPeriod1:height < 0")
Q34 = c("surveyPeriod2:height < 0")
Q35 = c("surveyPeriod1:biomass < 0")
Q36 = c("surveyPeriod2:biomass < 0")


# response: insects, predictors: grazing
hypTDbee         = hypothesis(modelResultsTDManagement[[1]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16))
hypTDbutterfly   = hypothesis(modelResultsTDManagement[[2]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypTDplanthopper = hypothesis(modelResultsTDManagement[[3]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 

hypPDbee         = hypothesis(modelResultsPDManagement[[1]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypPDbutterfly   = hypothesis(modelResultsPDManagement[[2]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypPDplanthopper = hypothesis(modelResultsPDManagement[[3]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 

hypFDbee         = hypothesis(modelResultsFDManagement[[1]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypFDbutterfly   = hypothesis(modelResultsFDManagement[[2]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypFDplanthopper = hypothesis(modelResultsFDManagement[[3]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 

# response: plants, predictors: grazing
hypVegSR         = hypothesis(modelResultsVegManagement[[1]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypVegFlower     = hypothesis(modelResultsVegManagement[[2]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypVegHeight     = hypothesis(modelResultsVegManagement[[3]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 
hypVegBiomass     = hypothesis(modelResultsVegManagement[[4]], c(Q1,Q2,Q3,Q4,Q5,Q6,Q7,Q8,Q9,Q10,Q11,Q12,Q13,Q14,Q15,Q16)) 


# response: insects, predictors: Vegetation 
hypTDbeeVeg         = hypothesis(modelResultsTDVegetation[[1]], c(Q17,Q18,Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,Q27,Q28))
hypTDbutterflyVeg   = hypothesis(modelResultsTDVegetation[[2]], c(Q17,Q18,Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,Q27,Q28)) 
hypTDplanthopperVeg = hypothesis(modelResultsTDVegetation[[3]], c(Q21,Q22,Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,Q35,Q36)) # height, biomass herbs


hypPDbeeVeg         = hypothesis(modelResultsPDVegetation[[1]], c(Q17,Q18,Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,Q27,Q28)) 
hypPDbutterflyVeg   = hypothesis(modelResultsPDVegetation[[2]], c(Q17,Q18,Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,Q27,Q28)) 
hypPDplanthopperVeg = hypothesis(modelResultsPDVegetation[[3]], c(Q21,Q22,Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,Q35,Q36)) 

hypFDbeeVeg         = hypothesis(modelResultsFDVegetation[[1]], c(Q17,Q18,Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,Q27,Q28)) 
hypFDbutterflyVeg   = hypothesis(modelResultsFDVegetation[[2]], c(Q17,Q18,Q19,Q20,Q21,Q22,Q23,Q24,Q25,Q26,Q27,Q28)) 
hypFDplanthopperVeg = hypothesis(modelResultsFDVegetation[[3]], c(Q21,Q22,Q27,Q28,Q29,Q30,Q31,Q32,Q33,Q34,Q35,Q36)) 
```

```{r}
hypTDbee$hypothesis$diversity =rep("TD",16)
hypTDbee$hypothesis$group =rep("bee",16)
hypTDbutterfly$hypothesis$diversity =rep("TD",16)
hypTDbutterfly$hypothesis$group =rep("butterfly",16)
hypTDplanthopper$hypothesis$diversity =rep("TD",16)
hypTDplanthopper$hypothesis$group =rep("planthopper",16)

hypPDbee$hypothesis$diversity =rep("PD",16)
hypPDbee$hypothesis$group =rep("bee",16)
hypPDbutterfly$hypothesis$diversity =rep("PD",16)
hypPDbutterfly$hypothesis$group =rep("butterfly",16)
hypPDplanthopper$hypothesis$diversity =rep("PD",16)
hypPDplanthopper$hypothesis$group =rep("planthopper",16)

hypFDbee$hypothesis$diversity =rep("FD",16)
hypFDbee$hypothesis$group =rep("bee",16)
hypFDbutterfly$hypothesis$diversity =rep("FD",16)
hypFDbutterfly$hypothesis$group =rep("butterfly",16)
hypFDplanthopper$hypothesis$diversity =rep("FD",16)
hypFDplanthopper$hypothesis$group =rep("planthopper",16)

hypVegSR$hypothesis$group =rep("SR",16)
hypVegFlower$hypothesis$group =rep("Flower",16)
hypVegHeight$hypothesis$group =rep("Height",16)
hypVegBiomass$hypothesis$group =rep("Biomass",16)

hypVegSR$hypothesis$diversity =rep("Veg",16)
hypVegFlower$hypothesis$diversity =rep("Veg",16)
hypVegHeight$hypothesis$diversity =rep("Veg",16)
hypVegBiomass$hypothesis$diversity =rep("Veg",16)

hypTDbeeVeg$hypothesis$diversity =rep("TD",12)
hypTDbeeVeg$hypothesis$group =rep("bee",12)
hypTDbutterflyVeg$hypothesis$diversity =rep("TD",12)
hypTDbutterflyVeg$hypothesis$group =rep("butterfly",12)
hypTDplanthopperVeg$hypothesis$diversity =rep("TD",12)
hypTDplanthopperVeg$hypothesis$group =rep("planthopper",12)


hypPDbeeVeg$hypothesis$diversity =rep("PD",12)
hypPDbeeVeg$hypothesis$group =rep("bee",12)
hypPDbutterflyVeg$hypothesis$diversity =rep("PD",12)
hypPDbutterflyVeg$hypothesis$group =rep("butterfly",12)
hypPDplanthopperVeg$hypothesis$diversity =rep("PD",12)
hypPDplanthopperVeg$hypothesis$group =rep("planthopper",12)

hypFDbeeVeg$hypothesis$diversity =rep("FD",12)
hypFDbeeVeg$hypothesis$group =rep("bee",12)
hypFDbutterflyVeg$hypothesis$diversity =rep("FD",12)
hypFDbutterflyVeg$hypothesis$group =rep("butterfly",12)
hypFDplanthopperVeg$hypothesis$diversity =rep("FD",12)
hypFDplanthopperVeg$hypothesis$group =rep("planthopper",12)




hypothesesResults = rbind(
hypTDbee$hypothesis,
hypTDbutterfly$hypothesis,
hypTDplanthopper$hypothesis,

hypPDbee$hypothesis,
hypPDbutterfly$hypothesis,
hypPDplanthopper$hypothesis,

hypFDbee$hypothesis,
hypFDbutterfly$hypothesis,
hypFDplanthopper$hypothesis,

hypVegSR$hypothesis,
hypVegFlower$hypothesis,
hypVegHeight$hypothesis,
hypVegBiomass$hypothesis,

hypTDbeeVeg$hypothesis,
hypTDbutterflyVeg$hypothesis,
hypTDplanthopperVeg$hypothesis,

hypPDbeeVeg$hypothesis,
hypPDbutterflyVeg$hypothesis,
hypPDplanthopperVeg$hypothesis,

hypFDbeeVeg$hypothesis,
hypFDbutterflyVeg$hypothesis,
hypFDplanthopperVeg$hypothesis
)

hypothesesResults$Hypothesis_fullname = hypothesesResults$Hypothesis
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:grazingTimeearly) > 0")]  = "SP1: early > control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:grazingTimelate) > 0")]  = "SP1: late > control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:grazingTimeearly) > 0")]  = "SP2: early > control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:grazingTimelate) > 0")]  = "SP2: late > control"

hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:grazingTimeearly) < 0")]  = "SP1: early < control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:grazingTimelate) < 0")]  = "SP1: late < control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:grazingTimeearly) < 0")]  = "SP2: early < control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:grazingTimelate) < 0")]  = "SP2: late < control"

hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:grazingTimeearly)-(surveyPeriod1:grazingTimelate) > 0")] = "SP1: early > late"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:grazingTimeearly)-(surveyPeriod2:grazingTimelate) > 0")] = "SP2: early > late"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(((surveyPeriod1:grazingTimeearly*0.5)+(surveyPeriod1:grazingTimelate*0.5))) > 0")] = 
  "SP1: grazing > control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(((surveyPeriod2:grazingTimeearly*0.5)+(surveyPeriod2:grazingTimelate*0.5))) > 0")] = 
  "SP2: grazing > control"

hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:grazingTimeearly)-(surveyPeriod1:grazingTimelate) < 0")] = "SP1: early < late"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:grazingTimeearly)-(surveyPeriod2:grazingTimelate) < 0")] = "SP2: early < late"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(((surveyPeriod1:grazingTimeearly*0.5)+(surveyPeriod1:grazingTimelate*0.5))) < 0")] = 
  "SP1: grazing < control"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(((surveyPeriod2:grazingTimeearly*0.5)+(surveyPeriod2:grazingTimelate*0.5))) < 0")] = 
  "SP2: grazing < control"

hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:nPlantSpecies) > 0")] = "SP1: SR plant > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:nPlantSpecies) > 0")] = "SP2: SR plant > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:nInflorescenceCoocc) > 0")]  = "SP1: Flower > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:nInflorescenceCoocc) > 0")]  = "SP2: Flower > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:coverHerbs) > 0")]  = "SP1: Cover herbs > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:coverHerbs) > 0")]  = "SP2: Cover herbs > intercept"

hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:nPlantSpecies) < 0")] = "SP1: SR plant < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:nPlantSpecies) < 0")] = "SP2: SR plant < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:nInflorescenceCoocc) < 0")]  = "SP1: Flower < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:nInflorescenceCoocc) < 0")]  = "SP2: Flower < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:coverHerbs) < 0")]  = "SP1: Cover herbs < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:coverHerbs) < 0")]  = "SP2: Cover herbs < intercept"



hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:biomass) > 0")] = "SP1: biomass > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:biomass) > 0")] = "SP2: biomass > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:height) > 0")] = "SP1: height > intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:height) > 0")] = "SP2: height > intercept"


hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:biomass) < 0")] = "SP1: biomass < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:biomass) < 0")] = "SP2: biomass < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod1:height) < 0")] = "SP1: height < intercept"
hypothesesResults$Hypothesis[which(hypothesesResults$Hypothesis_fullname=="(surveyPeriod2:height) < 0")] = "SP2: height < intercept"

hypothesesResults = arrange.vars(hypothesesResults, c("group"=1,"diversity"=2))

openxlsx::write.xlsx(hypothesesResults,paste("results/",gsub("-",".",Sys.Date()),"-Q1_Hypotheses.xlsx",sep=""),
                     firstRow = TRUE)
```

